---
title: "Star Wars 6- Text conversion"
author: "Samuel Rea"
date: "`r Sys.Date()`"
output: html_document
---
loading in the packages and setting working directory. Commented out currently
```{r}
#you may have to install some of the packages using the install.packages() function then library them
#setwd("/Users/samrea5/Desktop/uvafourthyear/second_semester/DS 4000 data science project/project1")
```


Now load in the text file convert it to another text file that we can later use for processing
```{r}
#reading in the 6th movie as an object
sw <- iconv(readLines("StarWars_EpisodeVI_script.txt", encoding = "UTF-8"), to = "ASCII", sub = " ")
#checking first 90 lines to make sure it is correct
sw[1:90]
#getting the length of the text file for loop
nlines = length(sw)
#the first line of dialogue begins on 70 so initialize the line counter to 70
i = 70
#these are space objects that help us crrectly identify character and dialogue lines in the loop
b15 = "               "
b30 = "                              "
#actual loop that goes through and makes a text file we can work with
writeLines("STAR WARS - EPISODE 6: RETURN OF THE JEDI", "EpisodeVI_dialogues.txt")
while (i <= nlines)
{
  # if empty line
  if (sw[i] == "") i = i + 1  # next line
  # if text line
  if (sw[i] != "")
  {
    # if uninteresting stuff
    if (substr(sw[i], 1, 1) != " ") {
      i = i + 1   # next line
    } else {
      if (nchar(sw[i]) < 10) {
        i = i + 1  # next line
      } else {
        if (substr(sw[i], 1, 5) != " " && substr(sw[i], 6, 6) != " ") {
          i = i + 1  # next line
        } else {
          # if character name
          if (substr(sw[i], 1, 30) == b30) 
          {
            if (substr(sw[i], 31, 31) != " ")
            {
              tmp_name = substr(sw[i], 31, nchar(sw[i], "bytes"))
              cat("\n", file="EpisodeVI_dialogues.txt", append=TRUE)
              cat(tmp_name, "", file="EpisodeVI_dialogues.txt", sep="\t", append=TRUE)
              i = i + 1        
            } else {
              i = i + 1
            }
          } else {
            # if dialogue
            if (substr(sw[i], 1, 15) == b15)
            {
              if (substr(sw[i], 16, 16) != " ")
              {
                tmp_diag = substr(sw[i], 16, nchar(sw[i], "bytes"))
                cat("", tmp_diag, file="EpisodeVI_dialogues.txt", append=TRUE)
                i = i + 1
              } else {
                i = i + 1
              }
            }
          }
        }
      }
    }    
  }
}
```

the conversion of the text file for star wars 6 is done. Now if the other r scripts have been run the correct text files should exist for all three movies and we can move to doing our actual analysis.
