---
title: "Master"
author: "Samuel Rea"
date: "`r Sys.Date()`"
output: html_document
---
IF you dont want to run the individual r markdown files, this one contains all the blocks of code needed to go from square 1 to the final product. This includes the preprocessing to the final saved graphs and results. IF you would like a more clear explination of each line of code please refer to the individual R scripts as they have much more information. 

Set your working directory and library any packages that might be needed for this analysis
```{r}
#setwd("/Users/samrea5/Desktop/uvafourthyear/second_semester/DS 4000 data science project/project1")
#install.packages()
library(tidyverse)
library(ggplot2)
library(tidytext)
library(dplyr)
library(stats)
library(SentimentAnalysis)
library(textdata)
library(tm)
library(wordcloud)
library(ggwordcloud)
library(stringr)
nrc<- tidytext::get_sentiments("nrc")
```


These first three blocks of code do all of the preprocessing of the data and get it to a text file that is useable for the analysis portion of the code
Star Wars 4
```{r}
sw <- iconv(readLines("StarWars_EpisodeIV_script.txt", encoding = "UTF-8"), to = "ASCII", sub = " ")
b10 = "          "
b20 = "                    "
nlines = length(sw)
i = 50
output_file <- file("EpisodeIV_dialogues.txt", "w")
while (i <= length(sw)) {
  # If empty line
  if (sw[i] == "") {
    i <- i + 1  # Move to the next line
  } else {
    # If script description or short line, move to the next line
    if (substr(sw[i], 1, 1) != " " || nchar(sw[i]) < 10) {
      i <- i + 1
    } else {
      # If character name
      if (substr(sw[i], 1, 20) == b20) {
        if (substr(sw[i], 21, 21) != " ") {
          tmp_name <- substr(sw[i], 21, nchar(sw[i], "bytes"))
          cat(tmp_name, "\n", file = output_file)
        }
        i <- i + 1
      }
      # If dialogue
      if (substr(sw[i], 1, 10) == b10) {
        if (substr(sw[i], 11, 11) != " ") {
          tmp_diag <- substr(sw[i], 11, nchar(sw[i], "bytes"))
          cat(tmp_diag, "\n", file = output_file)
        }
        i <- i + 1
      }
    }
  }
}

# Close the file connection
close(output_file)
```

Star Wars 5: preproccesing
```{r}
sw <- iconv(readLines("StarWars_EpisodeV_script.txt", encoding = "UTF-8"), to = "ASCII", sub = " ")
nlines = length(sw)
i = 30
current = FALSE
writeLines("STAR WARS - EPISODE 5: THE EMPIRE STRIKES BACK", "EpisodeV_dialogues.txt")
i = i + 1
while (i <= nlines)
{
  # if empty line
  if (sw[i] == "" || substr(sw[i], 1, 1) == " ") {
    current = FALSE
    i = i + 1  # next line
  } else {
    # EXTERIOR or INTERIOR (we don't want these lines)
    if (str_extract(sw[i], "\\w+") %in% c("INTERIOR", "EXTERIOR"))
    {
      current = FALSE
      i = i + 1
    } else {
      # good dialogue
      if (!current) {
        cat("\n", file="EpisodeV_dialogues.txt", append=TRUE)
        cat(sw[i], "", file="EpisodeV_dialogues.txt", append=TRUE)
        i = i + 1
        current = TRUE
      } else {
        cat("", sw[i], file="EpisodeV_dialogues.txt", append=TRUE)
        i = i + 1
        current = TRUE
      }
    }
  }
}
```

Star Wars Movie 6: Preprocessing
```{r}
sw <- iconv(readLines("StarWars_EpisodeVI_script.txt", encoding = "UTF-8"), to = "ASCII", sub = " ")
nlines = length(sw)
i = 70
b15 = "               "
b30 = "                              "
writeLines("STAR WARS - EPISODE 6: RETURN OF THE JEDI", "EpisodeVI_dialogues.txt")
while (i <= nlines)
{
  # if empty line
  if (sw[i] == "") i = i + 1  # next line
  # if text line
  if (sw[i] != "")
  {
    # if uninteresting stuff
    if (substr(sw[i], 1, 1) != " ") {
      i = i + 1   # next line
    } else {
      if (nchar(sw[i]) < 10) {
        i = i + 1  # next line
      } else {
        if (substr(sw[i], 1, 5) != " " && substr(sw[i], 6, 6) != " ") {
          i = i + 1  # next line
        } else {
          # if character name
          if (substr(sw[i], 1, 30) == b30) 
          {
            if (substr(sw[i], 31, 31) != " ")
            {
              tmp_name = substr(sw[i], 31, nchar(sw[i], "bytes"))
              cat("\n", file="EpisodeVI_dialogues.txt", append=TRUE)
              cat(tmp_name, "", file="EpisodeVI_dialogues.txt", sep="\t", append=TRUE)
              i = i + 1        
            } else {
              i = i + 1
            }
          } else {
            # if dialogue
            if (substr(sw[i], 1, 15) == b15)
            {
              if (substr(sw[i], 16, 16) != " ")
              {
                tmp_diag = substr(sw[i], 16, nchar(sw[i], "bytes"))
                cat("", tmp_diag, file="EpisodeVI_dialogues.txt", append=TRUE)
                i = i + 1
              } else {
                i = i + 1
              }
            }
          }
        }
      }
    }    
  }
}
```


Now that the preprocessing is done we can do the exact same analysis as the analysis R script. Again if more detail is wanted on the code please refer to the individual R scripts. It is much easier to troubleshoot any issues given there is code explinations
Creating data frames
```{r}
#Starwars 4
text_lines <- readLines("EpisodeIV_dialogues.txt")


# Initialize vectors to store character names and dialogues
character_names <- c()
dialogues <- c()

# Initialize variables to keep track of character name and dialogue
current_character <- NULL
current_dialogue <- ""

# Iterate through each line of the text
for (line in text_lines) {
  # Check if the line is in all caps (indicating a character name)
  if (toupper(line) == line) {
    # If there was a previous character, store its dialogue
    if (!is.null(current_character)) {
      character_names <- c(character_names, current_character)
      dialogues <- c(dialogues, current_dialogue)
    }
    # Update current character and reset dialogue
    current_character <- line
    current_dialogue <- ""
  } else {
    # If not in all caps, append to current dialogue
    current_dialogue <- paste(current_dialogue, line, sep = " ")
  }
}

# Append the last character's dialogue
if (!is.null(current_character)) {
  character_names <- c(character_names, current_character)
  dialogues <- c(dialogues, current_dialogue)
}
# Create a data frame from character names and dialogues
starwars4 <- data.frame(Character = character_names, Dialogue = dialogues, stringsAsFactors = FALSE)

#starwars 5
system("wc -l EpisodeV_dialogues.txt")

# get vector of character names
SW5_chars = system("tail -n839 EpisodeV_dialogues.txt | cut -f1 -d':'", intern=TRUE)
# get vector of dialogue lines
SW5_diags = system("tail -n839 EpisodeV_dialogues.txt | cut -f2 -d':'", intern=TRUE)

# check character names
table(SW5_chars)
# remove apostrophes voices
SW5_chars = gsub("'S VOICE", "", SW5_chars)

# remove strings between parenthesis in dialogues
SW5_diags = gsub("\\((.*?)\\)", "", SW5_diags)

# remove extra white spaces at the beginning and the end of dialogues
SW5_diags = gsub("^\\s+", "", SW5_diags)
SW5_diags = gsub("\\s+$", "", SW5_diags)

# join characters and dialogues in one table
SW5 = cbind(character=SW5_chars, dialogue=SW5_diags)
# save SW5 in file 'SW_EpisodeV.txt'
write.table(SW5, file="SW_EpisodeV.txt")

# if you want to check the data table
starwars5 = read.table("SW_EpisodeV.txt")



#starwars 6

system("wc -l EpisodeVI_dialogues.txt")

# get vector of character names
SW6_chars = system("tail -n676 EpisodeVI_dialogues.txt | cut -f1", intern=TRUE)
# get vector of dialogue lines
SW6_diags = system("tail -n676 EpisodeVI_dialogues.txt | cut -f2", intern=TRUE)

# check character names
table(SW6_chars)
# remove strings between parenthesis in SW6_chars
SW6_chars = gsub("\\((.*?)\\)", "", SW6_chars)
# remove extra white spaces in SW6_chars
SW6_chars = gsub("\\s+$", "", SW6_chars)

# remove strings between parenthesis in dialogues
SW6_diags = gsub("\\((.*?)\\)", "", SW6_diags)
# remove extra white spaces at the beginning of dialogues
SW6_diags = gsub("^\\s+", "", SW6_diags)

# remove last line (useless)
SW6_chars = SW6_chars[-length(SW6_chars)]
SW6_diags = SW6_diags[-length(SW6_diags)]

# fix DEATH STAR CONTROLLER dialogue (this is the only exception)
SW6_diags[2] = SW6_diags[3]

# join characters and dialogues in one table
SW6 = cbind(character=SW6_chars[-3], dialogue=SW6_diags[-3])

# save SW6 in file 'SW_EpisodeVI.txt'
write.table(SW6, file="SW_EpisodeVI.txt")

# if you want to check the data table
starwars6 = read.table("SW_EpisodeVI.txt")
```
THis is the basic sentiment analysis on the movies using the nrc sentiment dictionary. How this code works is it tokenizes the text in the data frame then joins it to the sentiments of the NRC dataframe. Then it just counts the number of occurances for each sentiment in the attached dataframe. THis gives us the counts of these sentiments. Finally this section of code produces a graph that shows the count of each sentiment. There is also a graph produced for movie 6 that shows the emotional language used by each character. Again this section of code is for Movie 6
```{r}
#this is for the 6th starwars movie
movie_script_tokens6 <- starwars6 %>%
  unnest_tokens(word, dialogue)

# Step 2: Get sentiment scores using NRC sentiment dictionary
sentiments6 <- get_sentiments("nrc")

# Step 3: Join sentiment scores with the tokenized text
movie_sentiments6 <- movie_script_tokens6 %>%
  inner_join(sentiments6)

# Step 4: Count the occurrences of each sentiment by character
sentiment_counts6 <- movie_sentiments6 %>%
  count(character, sentiment) %>%
  ungroup() %>%
  mutate(sentiment = factor(sentiment, levels = rev(names(sort(table(sentiment), decreasing = TRUE)))))

# Step 5: Plot the results
sentimentcharacter6<-ggplot(sentiment_counts6, aes(x = character, y = n, fill = sentiment)) +
  geom_bar(stat = "identity", position = "stack") +
  theme_minimal() +
  labs(title = "Sentiment Analysis of Movie Script",
       x = "Character",
       y = "Frequency",
       fill = "Sentiment") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  coord_flip()

# Step 6: Output the results
#print(sentiment_counts)
#this is just emotions that are used in the movie and how common/frequent they are
# Step 2: Get sentiment scores using NRC sentiment dictionary
sentiments <- get_sentiments("nrc")

# Step 3: Join sentiment scores with the tokenized text
movie_script_tokens6 <- starwars6 %>%
  unnest_tokens(word, dialogue)

# Step 4: Count the occurrences of each sentiment
sentiment_counts6 <- movie_sentiments6 %>%
  count(sentiment) %>%
  ungroup() %>%
  mutate(sentiment = factor(sentiment, levels = rev(names(sort(table(sentiment), decreasing = TRUE)))))

# Step 5: Plot the results as lines
sentimentvisual6<-ggplot(sentiment_counts6, aes(x = sentiment, y = n)) +
  geom_bar(stat = "identity", fill = "blue") +
  theme_minimal() +
  labs(title = "Frequency of Emotions in Movie Script: Star Wars 6",
       x = "Emotion",
       y = "Frequency") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```




THis is the basic sentiment analysis on the movies using the nrc sentiment dictionary. How this code works is it tokenizes the text in the data frame then joins it to the sentiments of the NRC dataframe. Then it just counts the number of occurances for each sentiment in the attached dataframe. THis gives us the counts of these sentiments. Finally this section of code produces a graph that shows the count of each sentiment. There is also a graph produced for movie 6 that shows the emotional language used by each character. Again this section of code is for Movie 5
```{r}
#this is for the 5th starwars movie
#nrc<- tidytext::get_sentiments("nrc")
movie_script_tokens5 <- starwars5 %>%
  unnest_tokens(word, dialogue)

# Step 2: Get sentiment scores using NRC sentiment dictionary
sentiments5 <- get_sentiments("nrc")

# Step 3: Join sentiment scores with the tokenized text
movie_sentiments5 <- movie_script_tokens5 %>%
  inner_join(sentiments5)

# Step 4: Count the occurrences of each sentiment by character
sentiment_counts5 <- movie_sentiments5 %>%
  count(character, sentiment) %>%
  ungroup() %>%
  mutate(sentiment = factor(sentiment, levels = rev(names(sort(table(sentiment), decreasing = TRUE)))))

# Step 5: Plot the results
sentimentcharacter5<-ggplot(sentiment_counts5, aes(x = character, y = n, fill = sentiment)) +
  geom_bar(stat = "identity", position = "stack") +
  theme_minimal() +
  labs(title = "Sentiment Analysis of Movie Script",
       x = "Character",
       y = "Frequency",
       fill = "Sentiment") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  coord_flip()

# Step 6: Output the results
#print(sentiment_counts)
#this is just emotions that are used in the movie and how common/frequent they are
# Step 2: Get sentiment scores using NRC sentiment dictionary
sentiments <- get_sentiments("nrc")

# Step 3: Join sentiment scores with the tokenized text
movie_script_tokens5 <- starwars5 %>%
  unnest_tokens(word, dialogue)

# Step 4: Count the occurrences of each sentiment
sentiment_counts5 <- movie_sentiments5 %>%
  count(sentiment) %>%
  ungroup() %>%
  mutate(sentiment = factor(sentiment, levels = rev(names(sort(table(sentiment), decreasing = TRUE)))))

# Step 5: Plot the results as lines
sentimentvisual5<-ggplot(sentiment_counts5, aes(x = sentiment, y = n)) +
  geom_bar(stat = "identity", fill = "blue") +
  theme_minimal() +
  labs(title = "Frequency of Emotions in Movie Script: Star Wars 5",
       x = "Emotion",
       y = "Frequency") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

THis is the basic sentiment analysis on the movies using the nrc sentiment dictionary. How this code works is it tokenizes the text in the data frame then joins it to the sentiments of the NRC dataframe. Then it just counts the number of occurances for each sentiment in the attached dataframe. THis gives us the counts of these sentiments. Finally this section of code produces a graph that shows the count of each sentiment. There is also a graph produced for movie 6 that shows the emotional language used by each character. Again this section of code is for Movie 4
```{r}
#this is for the 4th starwars movie
#nrc<- tidytext::get_sentiments("nrc")
movie_script_tokens4 <- starwars4 %>%
  unnest_tokens(word, Dialogue)

# Step 2: Get sentiment scores using NRC sentiment dictionary
sentiments4 <- get_sentiments("nrc")

# Step 3: Join sentiment scores with the tokenized text
movie_sentiments4 <- movie_script_tokens4 %>%
  inner_join(sentiments4)

# Step 4: Count the occurrences of each sentiment by character
sentiment_counts4 <- movie_sentiments4 %>%
  count(Character, sentiment) %>%
  ungroup() %>%
  mutate(sentiment = factor(sentiment, levels = rev(names(sort(table(sentiment), decreasing = TRUE)))))

# Step 5: Plot the results
sentimentcharacter4<-ggplot(sentiment_counts4, aes(x = Character, y = n, fill = sentiment)) +
  geom_bar(stat = "identity", position = "stack") +
  theme_minimal() +
  labs(title = "Sentiment Analysis of Movie Script",
       x = "Character",
       y = "Frequency",
       fill = "Sentiment") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  coord_flip()

# Step 6: Output the results
#print(sentiment_counts)
#this is just emotions that are used in the movie and how common/frequent they are
# Step 2: Get sentiment scores using NRC sentiment dictionary
sentiments <- get_sentiments("nrc")

# Step 3: Join sentiment scores with the tokenized text
movie_script_tokens4 <- starwars4 %>%
  unnest_tokens(word, Dialogue)

# Step 4: Count the occurrences of each sentiment
sentiment_counts4 <- movie_sentiments4 %>%
  count(sentiment) %>%
  ungroup() %>%
  mutate(sentiment = factor(sentiment, levels = rev(names(sort(table(sentiment), decreasing = TRUE)))))

# Step 5: Plot the results as lines
sentimentvisual4<-ggplot(sentiment_counts4, aes(x = sentiment, y = n)) +
  geom_bar(stat = "identity", fill = "blue") +
  theme_minimal() +
  labs(title = "Frequency of Emotions in Movie Script: Star Wars 4",
       x = "Emotion",
       y = "Frequency") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))


```


now that we have sentiment scores for each of the movies we calculated frequency and the ratio of the words used in each movie. That is what this nex block of code does.
```{r}

total5 <- sum(sentiment_counts5$n)
sentiment_counts5 <- sentiment_counts5 %>% mutate(ratio = n/total5)

total6 <- sum(sentiment_counts6$n)
sentiment_counts6 <- sentiment_counts6 %>% mutate(ratio = n/total6)


total4 <- sum(sentiment_counts4$n)
sentiment_counts4 <- sentiment_counts4 %>% mutate(ratio = n/total4)
```

After we calculate these ratios we join them into a master data frame that allows us to do all of our analysis.
```{r}
final_ratios<-sentiment_counts4[, c("sentiment", "ratio")] %>% rename(ratio4 = ratio) %>% 
  inner_join(sentiment_counts5) %>% rename(ratio5 = ratio) %>% select(-n) %>%
  inner_join(sentiment_counts6) %>% rename(ratio6 = ratio) %>% select(-n) %>%
  mutate(ratio4 = ratio4*100, ratio5 = ratio5*100, ratio6=ratio6*100) 



```


This section runs a chi-squared for proportional counts of words categorized by emotion and just straight counts of words. 
```{r}
# Lists to store chi-square test results for counts
count_chi_square_stats <- list()
count_chi_square_pvalues <- list()

# Lists to store chi-square test results for ratios
ratio_chi_square_stats <- list()
ratio_chi_square_pvalues <- list()

# Unique emotions in the data frames
emotions <- unique(c(sentiment_counts4$sentiment, sentiment_counts5$sentiment, sentiment_counts6$sentiment))

# Iterate over each emotion
for (emotion in emotions) {
  # Subset counts data for the current emotion from each movie
  counts_data <- list(sentiment_counts4[sentiment_counts4$sentiment == emotion, "n"],
                      sentiment_counts5[sentiment_counts5$sentiment == emotion, "n"],
                      sentiment_counts6[sentiment_counts6$sentiment == emotion, "n"])
  
  # Perform chi-square test for counts
  count_chi_square_results <- chisq.test(do.call(rbind, counts_data))
  
  # Store test statistics and p-values
  count_chi_square_stats[[emotion]] <- count_chi_square_results$statistic
  count_chi_square_pvalues[[emotion]] <- count_chi_square_results$p.value
  
  # Subset ratios data for the current emotion from each movie
  ratios_data <- list(sentiment_counts4[sentiment_counts4$sentiment == emotion, "ratio"],
                      sentiment_counts5[sentiment_counts5$sentiment == emotion, "ratio"],
                      sentiment_counts6[sentiment_counts6$sentiment == emotion, "ratio"])
  
  # Perform chi-square test for ratios
  ratio_chi_square_results <- chisq.test(do.call(rbind, ratios_data))
  
  # Store test statistics and p-values
  ratio_chi_square_stats[[emotion]] <- ratio_chi_square_results$statistic
  ratio_chi_square_pvalues[[emotion]] <- ratio_chi_square_results$p.value
}

# Combine results into data frames
count_results_df <- data.frame(emotion = emotions,
                               chi_square_statistic = unlist(count_chi_square_stats),
                               p_value = unlist(count_chi_square_pvalues))

ratio_results_df <- data.frame(emotion = emotions,
                               chi_square_statistic = unlist(ratio_chi_square_stats),
                               p_value = unlist(ratio_chi_square_pvalues))
```

this makes word clouds for each movie to give the audience a better idea of the most common word used and to give a better understnading of the dialogue used in the movies.
```{r}
#Star Wars #4
corpus4 <- Corpus(VectorSource(movie_sentiments4$word))
corpus4 <- tm_map(corpus4, content_transformer(tolower))
corpus4 <- tm_map(corpus4, removePunctuation)
corpus4 <- tm_map(corpus4, removeNumbers)
corpus4 <- tm_map(corpus4, removeWords, stopwords("english"))
tdm4 <- TermDocumentMatrix(corpus4)
m4 <- as.matrix(tdm4)
word_freq4 <- sort(rowSums(m4), decreasing = TRUE)
word_freq_df4 <- data.frame(word = names(word_freq4), freq = word_freq4)
top_words4 <- head(word_freq_df4, 40)

# Create the word cloud plot with colors and title for Star Wars 4
wordcloud_plot4 <- ggplot(top_words4, aes(label = word, size = freq, color = word)) +
  geom_text_wordcloud() +  # Using the correct function
  scale_size_area(max_size = 20) +
  scale_color_manual(values = rainbow(length(unique(top_words4$word)))) +  # Setting colors
  theme_void() +
  ggtitle("Star Wars 4") +  # Adding title
  theme(plot.title = element_text(hjust = 0.5))  # Center the title

print(wordcloud_plot4)


#Star Wars Movie #5
corpus5 <- Corpus(VectorSource(movie_sentiments5$word))
corpus5 <- tm_map(corpus5, content_transformer(tolower))
corpus5 <- tm_map(corpus5, removePunctuation)
corpus5 <- tm_map(corpus5, removeNumbers)
corpus5 <- tm_map(corpus5, removeWords, stopwords("english"))
tdm5 <- TermDocumentMatrix(corpus5)
m5 <- as.matrix(tdm5)
word_freq5 <- sort(rowSums(m5), decreasing = TRUE)
word_freq_df5 <- data.frame(word = names(word_freq5), freq = word_freq5)
top_words5 <- head(word_freq_df5, 40)

# Create the word cloud plot with colors and title for Star Wars 5
wordcloud_plot5 <- ggplot(top_words5, aes(label = word, size = freq, color = word)) +
  geom_text_wordcloud() +  # Using the correct function
  scale_size_area(max_size = 20) +
  scale_color_manual(values = rainbow(length(unique(top_words5$word)))) +  # Setting colors
  theme_void() +
  ggtitle("Star Wars 5") +  # Adding title
  theme(plot.title = element_text(hjust = 0.5))  # Center the title

print(wordcloud_plot5)



#Star Wars #6
corpus6 <- Corpus(VectorSource(movie_sentiments6$word))
corpus6 <- tm_map(corpus6, content_transformer(tolower))
corpus6 <- tm_map(corpus6, removePunctuation)
corpus6 <- tm_map(corpus6, removeNumbers)
corpus6 <- tm_map(corpus6, removeWords, stopwords("english"))
tdm6 <- TermDocumentMatrix(corpus6)
m6 <- as.matrix(tdm6)
word_freq6 <- sort(rowSums(m6), decreasing = TRUE)
word_freq_df6 <- data.frame(word = names(word_freq6), freq = word_freq6)
top_words6 <- head(word_freq_df6, 40)

# Create the word cloud plot with colors and title for Star Wars 6
wordcloud_plot6 <- ggplot(top_words6, aes(label = word, size = freq, color = word)) +
  geom_text_wordcloud() +  # Using the correct function
  scale_size_area(max_size = 20) +
  scale_color_manual(values = rainbow(length(unique(top_words6$word)))) +  # Setting colors
  theme_void() +
  ggtitle("Star Wars 6") +  # Adding title
  theme(plot.title = element_text(hjust = 0.5))  # Center the title

print(wordcloud_plot6)
```

This final chunk of code is just saving graphs and data frames. for access at a later date
```{r}

ggsave('wordcloud4.jpg', plot = wordcloud_plot4)
ggsave('wordcloud5.jpg', plot = wordcloud_plot5)
ggsave('wordcloud6.jpg', plot = wordcloud_plot6)

ggsave('sentimentvisual4.jpg', plot = sentimentvisual4)
ggsave('sentimentvisual5.jpg', plot = sentimentvisual5)
ggsave('sentimentvisual6.jpg', plot = sentimentvisual6)

ggsave('sentimentcharacter4.jpg', plot = sentimentcharacter4)
ggsave('sentimentcharacter5.jpg', plot = sentimentcharacter5)
ggsave('sentimentcharacter6.jpg', plot = sentimentcharacter6)
write.csv(count_results_df, "count_results.csv", row.names = FALSE)
write.csv(ratio_results_df, "ratio_results.csv", row.names = FALSE)
```
